BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-02 tex/3-algorithms.tex
Fix some todos

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation}
% html extraction is not trival
Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \TODO{ref to W3C standards}.
For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}.
More recently, specifications such as Microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}\TODO{FIX REF!}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.

\TODO{Assumption is not a good word, we are based on facts from previous work.
I suggest that you restructure this part as follows:

Having blogs as our target websites, we are taking into account  the following facts that play a central role in the extraction process.

1. "Blog is a kind of web page [with] frequent, usually brief posts, with the immediacy of reverse chronological order" (+ ref to BlogForever D2.2: BlogForever Data Model 
https://zenodo.org/record/7488/files/BlogForever\_D2\_2WeblogDataModel.pdf

2. blogs provide web feeds: structured and standardised views of the most recent blog posts.

3. Web feeds contain information regarding the latest blog posts (usually 10 or 20 entries) + ref

4. posts of the same blog share a similar HTML structure.

Consequently, in order to effectively archive old blog content, it is necessary to download and process pages beyond the ones referenced in web feeds.
}

@@

In addition, having an independent computation for each input makes the algorithm \emph{embarrassingly parallel}\comment{it's a coined term, so it's fine, but should we have a reference here? -> Can't find a good one..}: iterations of the outer loop can trivially be executed by multiple threads.

@@

% string similarity
Unsurprisingly, the choice of the string similarity algorithm greatly influences the running time and precision of the extraction process. We chose the Sørensen–Dice coefficient similarity\cite{dice1945}, which, to the best of our knowledge\comment{maybe remove this? it weakens our choice a bit. -> at the same time it might not be the only one...}, is the only string similarity algorithm fulfilling the following criteria:

@@

% Linear reformulation
We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement $memoization$ \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams. This way we avoid serializing HTML subtrees for each bigram computation and we can guarantee that each character of the HTML page will be read at most once during the bigrams computation. Thus, the cumulated time needed to compute bigrams of \emph{node.text} is linear.

@@

% Dates, authors
Dates are affected by the same duplication issue, as well as the inconsistence of format between web feeds and web pages. Our solution is to use multiple \emph{target} strings, while extending the rule that we previously described for author extraction. For instance, if the feed indicates that a post was published on
\stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will create a rule that extracts one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on. We use a list of \TODO{none so far :(} target date formats that was empirically built during our experiments. While this list is certainly not exhaustive, our approach using string similarity on multiple target dates is robust and tolerant to format variations. We do not, so far, support dates in multiple languages but English was sufficient for our experiments.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation}
% html extraction is not trival
Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}. For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. More recently, specifications such as Microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation\cite{brianwilson2008-a}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.

\TODO{Assumption is not a good word, we are based on facts from previous work.}
% I suggest that you restructure this part as follows:

% Having blogs as our target websites, we are taking into account  the following facts that play a central role in the extraction process.

% 1. "Blog is a kind of web page [with] frequent, usually brief posts, with the immediacy of reverse chronological order" (+ ref to BlogForever D2.2: BlogForever Data Model
% https://zenodo.org/record/7488/files/BlogForever\_D2\_2WeblogDataModel.pdf

% 2. blogs provide web feeds: structured and standardised views of the most recent blog posts.

% 3. Web feeds contain information regarding the latest blog posts (usually 10 or 20 entries) + ref

% 4. posts of the same blog share a similar HTML structure.

% Consequently, in order to effectively archive old blog content, it is necessary to download and process pages beyond the ones referenced in web feeds.}

@@

In addition, having an independent computation for each input makes the algorithm \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed by multiple threads.

@@

% string similarity
Unsurprisingly, the choice of the string similarity algorithm greatly influences the running time and precision of the extraction process. We chose the Sørensen–Dice coefficient similarity\cite{dice1945}, which, to the best of our knowledge, is the only string similarity algorithm fulfilling the following criteria:

@@

% Linear reformulation
We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement \emph{memoization} over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams. This way we avoid serializing HTML subtrees for each bigram computation and we can guarantee that each character of the HTML page will be read at most once during the bigrams computation. Thus, the cumulated time needed to compute bigrams of \emph{node.text} is linear.

@@

% Dates, authors
Dates are affected by the same duplication issue, as well as the inconsistence of format between web feeds and web pages. Our solution is to use multiple \emph{target} strings, while extending the rule that we previously described for author extraction. For instance, if the feed indicates that a post was published on
\stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will create a rule that extracts one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on. We use a total of 8 target date formats that was empirically built during our experiments. While this list is certainly not exhaustive, our approach using string similarity on multiple target dates is tolerant to small variations. So far we do not support dates in multiple languages, but adding new target formats base and languages detection would certainly by a possible extension of our date extraction algorithm.

### 2013-12-02 tex/4-techniques.tex
Fix some todos

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case. Finally we will talk about deployement to scalable, fault resilient distributed architecture.

@@

% The solution
To support blogs with JavaScript generated content, we embed a full web browser into the crawler. After considering multiple option, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities. The JavaScript rendering is done as the very first step of web page processing. Extracting blog post content, comments or images therefore works equally well on both blogs with JavaScript generated content and traditional HTML-only blogs.

@@

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After downloading its HTML\TODO{rephrase!}, a web page is packed into an \emph{Item} and sent through the following pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download medias
  \item Propagate resulting records to the Invenio back-end
\end{enumerate}
This pipeline design, often called \emph{pipes and filters pattern} \cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabeling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
% Into, blog post identification
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used to identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

% download priority heuristic
In order to efficiently deal with blogs with a large number of non-blog-post pages, this blog post identification mechanism is not sufficient. Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog post pages to search for additional blog posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain. This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next. Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

Due to space constraints, more precise description and evaluation of these two components where not included in this paper.
\TODO{Again these things are great and you should write a lot more, instead of explaining Javascript rendering so much in 4.1  (it is trivial compared to these nice algorithms).}

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
\TODO{merge with 4.3, remove all the usless things. I believe that scalability should be removed from here and included in future work in the end.

Also, everyone knows what scalability is and we don't have a lot of space as we said earlier :)
The Reactive manifesto is not necessary...}
When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind. Citing the Reactive Manifesto \cite{thereactivemanifesto2013}:

\begin{quoting}
  If one of these layers does not participate—making blocking calls to the database, relying on shared mutable state, calling out to expensive synchronous operations—then the whole pipeline stalls and users will suffer through increased latency and reduced scalability.
\end{quoting}

At the time of writing we did not had the chance to work on the deployment of the BlogForever project on a distributed environment. However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, where designed to be usable as part of an event-driven, scalable and fault resilient distributed system.

\Anotecontent{noteC}{Blogs that do not provide a global comment feed need a special handling. If comment feeds are attached to each blog post, periodically checking for comment updates might be done with a reasonable cost. However, in the worst case where no comment feeds are provided, the only solution is to periodically do a full crawl of the blog to capture new comments.}

Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities. \emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog posts, comments and medias. Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{noteC} and a time, and returns records of objects that where emitted after the given time. The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably.

Regarding the asynchronous architecture, Scrapy is build upon Twisted\cite{twisted2013}, an event-driven networking framework for Python. Scrapy also provides a built-in service to start spiders with an HTTP JSON API. With these tools in hand, the only component to implement in order to achieve a scalable and fault resilient distributed crawling system is an entity to keep track of available crawlers and does appropriate load balancing between them.

>>>>

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case. Finally we will talk about deployment to scalable, fault resilient distributed architecture.

@@

% The solution
To support blogs with JavaScript generated content, we embed a full web browser into the crawler. After considering multiple option, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities. The JavaScript rendering is done as the very first step of web page processing. Extracting blog post content, comments or medias therefore works equally well on both blogs with JavaScript generated content and traditional HTML-only blogs.

@@

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After beeing downloaded and identified as blog posts (details in subsection \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download medias
  \item Propagate resulting records to the Invenio back-end
\end{enumerate}
This pipeline design, often called \emph{pipes and filters pattern} \cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}\label{enrichingscrapy}
% Into, blog post identification
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used to identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

% download priority heuristic
In order to efficiently deal with blogs with a large number of non-blog-post pages, this blog post identification mechanism is not sufficient. Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog post pages to search for additional blog posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain. This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visit next. Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind\cite{thereactivemanifesto2013}. At the time of writing we did not had the chance to work on the deployment of the BlogForever project on a distributed environment. However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.

To achieve this property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. Indeed, from a high level viewpoint, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}(\cdot)$ designates the powerset. By delegating all shared mutable state to the backend system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.

### 2013-12-02 tex/5-evaluation.tex
Fix some todos

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{}. These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assumptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).

@@

On our test-set algorithm~\ref{extractionAlgo} outperformed the concurrence by 4.9\% margin on content extraction and a 10.1\% margin on title extraction. It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web pages. Contrariwise,\TODO{is this transition ok?} our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages. Therefore, results showed in table \ref{precisionTable} should not be interpreted as general evaluation of quality of the different projects, but simply mean that our approach is more suitable when working with blogs.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{python-readability2011}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{goose2012}. These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assumptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).

@@

On our test-set algorithm~\ref{extractionAlgo} outperformed the concurrence by 4.9\% margin on content extraction and a 10.1\% margin on title extraction. It is important to stress that Readability, Boilerpipe and Goose rely on generic techniques such word density, paragraph clustering and heuristics on HTML tagging conventions, which are designed to work for any type of web pages. Contrariwise, our algorithm is only suitable for pages with associated web feeds, as these provide the reference data which we search for in HTML trees of pages. Therefore, results showed in table \ref{precisionTable} should not be interpreted as general evaluation of quality of the different projects, but simply mean that our approach is more suitable when working with blogs.

### 2013-12-02 tex/runningtimeFigure.tex
Fix some todos

\begin{figure}[ht]
  \hspace{-33pt}
  \begin{gnuplot}
    set terminal epslatex color
    set size 0.765
    set size ratio 0.618

@@

    plot 'data/runningtime.txt'\
       u 0:1 smooth cumulative w lines linewidth 5 title 'Algorithm \ref{extractionAlgo}',\
    '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
    '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
    '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose'
  \end{gnuplot}
\end{figure}

% \begin{figure}[ht]
%   \vspace{-59pt}
%   \hspace{-29pt}
%   \begin{gnuplot}
%     set terminal epslatex color
%     set size 0.725
%     set size ratio 0.618

%     set ylabel 'Cumulated running time (sec.)' offset 1.3
%     set xlabel 'Processed pages'

%     set yrange [0:55]
%     set xrange [0:65]

%     set arrow from 15,graph(0,0) to 15,graph(1,1) nohead linecolor rgb 'grey' linetype 2

%     plot 'data/runningtime.txt'\
%        u 0:1 smooth cumulative w lines linewidth 5 title 'Algorithm \ref{extractionAlgo}',\
%     '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
%     '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
%     '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose'
%   \end{gnuplot}
% \end{figure}

>>>>

\begin{figure}[ht]
  \hspace{-34pt}
  \begin{gnuplot}
    set terminal epslatex color
    set size 0.76
    set size ratio 0.618

@@

    plot 'data/runningtime.txt'\
       u 0:1 smooth cumulative w lines linewidth 5 title 'Our approach',\
    '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
    '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
    '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose'
  \end{gnuplot}
\end{figure}
